Tor's Usability for Censorship Circumvention

### 2016-04-04 pets2017-paper/pets2017-paper.tex
add background intro

\section{Background}

>>>>

\section{Background} 
In this section, we talk about network components that circumvent censorship, Tor Browser 5.0.3 configuration interface that guides users to configure those network components to make a connection to the Tor Network, and the current state of Internet censorship which had impact on both the deployed and redesigned configuration interface.
